The glEnd() of Zelda

### 2016-03-13 trunk/smeight/paper/paper.tex
start on paper

\begin{figure*}[p]
\begin{center}
\includegraphics[width=3.5in]{link3d}
\end{center}\vspace{-0.1in}
\caption{Histogram of one million experiments.} \label{figure:link3d}
\smallskip
The top group is the
% } 
\end{figure*}

>>>>

{\bf 1986. Hyrule.}\quad The Legend of {\it frickin'}~Zelda for the Nintendo {\it freakin'}~Entertainment System. Need I say more? A {\it god damn} \uline{gold cartridge}. Fortunes made just from saving the gold cartridge and melting it down to make gold teeth grilles, after carefully extracting the even more precious ROM inside. A die-cut hole in the box so that you could get a peek of the cartridge and presage that you were getting some solid gold. A die cut little window that you could palpate through the wrapping paper on Christmas~Eve, presaging some epic thumb blisters in store for the coming weeks. Koji {\it freckin'} Kondo. Koji Kondo whipping up a nice 8-bit arrangement of Bol\'ero as the theme music until realizing at the last minute that this music was copyrighted\footnote{Perhaps ironic, since Ravel's {Bol\'ero} itself was composed as a result of Ravel getting cop-blocked.\cite{wikipedia2016bolero} And surely some Zelda knock-off since then has included a Muzak ersatz of the Zelda theme! What is the longest documented sequence of compositions due to Copyright restrictions?} and so instead composing its epic theme in {\it one day}??

A gold cartridge that contained ROMs and a little swallowable battery to keep the onboard SRAM powered up so that it could retain your epic save game. A battery designed to last 70~years. Nothing could cause you to lose your save game, even once you were half way through the Second Quest. Unless your little brother starts a completely new game and saves over your slot, earning him one of the most righteously deserved clobberings this side of Inigo Montoya. Saves right on top of your slot with a player called just \verb+A   +. Right over your slot, erasing it, and hasn't even picked up the {\it sword} yet. Saves right over yours even though there are TWO OTHER UNUSED SLOTS and you even wisely put your game in the third slot {\it exactly to avoid this kind of calamity}.

Need I say more? Shall I say it?

technical limitations...
Like looking at tree people with polyhedra for hands is some kind of ...

\begin{figure*}[p]
\begin{center}
\includegraphics[width=3.5in]{link3d}
\end{center}\vspace{-0.1in}
\caption{Technical diagram of mathematical equations.} \label{figure:link3d}
\smallskip
% caption can go here...
% } 
\end{figure*}

\nocite{murphy2013first}
